Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-08-12 Latex/journal_v1/V5/pr.tex
add figure

Virtualization technique for RAN and core is one of the exciting topics.  
In \cite{SystemCostMinimization,guo2016exploiting}, the authors solve the problem of obtaining beamforming and VMs activation in a C-RAN system with limited fronthaul capacity. 
This paper aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint. 
Also, transmission and processing delay are modeled based on M/M/1 queuing theory to guarantee delay for the UEs.
 In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also, the association of RRH to the UE is considered and solved using innovative methods.
In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
\subsection{Main Contribution}
This study aims to optimize baseband resource allocation (power allocation, PRB allocation, and O-RUs association) and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform. In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follow:
\begin{itemize}
\item In this paper, a network slicing model is depicted for three different types of services introduced in 5G (URLLC, eMBB, and mMTC). The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for a different types of services with specific QoS. 
\item The desired QoS conditions such as delay and throughput are considered for different types of services. We formulate the end-to-end mean delay of the system based on the number of activated VNFs and each user's throughput.
We consider the limited fronthaul capacity and accurately obtain the power and the capacity of each O-RU based on the quantization noise.
We model the interference of neighboring O-RU and formulate the actual throughput
for different types of services. We model the throughput of URLLC and mMTC based on their short packet transmission.
\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
We perform a two-step iterative algorithm to solve it.
The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
\end{itemize}

@@

Also, \eqref{c13} shows that the rate of each UE requesting each type of service (eMBB, URLLC, and mMTC) is more than a threshold, respectively.

@@

So the the aggregate throughput is ascending function concerning the number of iterations and it will converge to the optimal solution.

@@

In this section, numerical results for the main problem are depicted to evaluate the performance of the algorithms using the Monte-Carlo method. We consider three network slices for eMBB, URLLC, and mMtc services.

@@

@@

 Maximum transmit Power of each O-RU & 38dBm \\

@@

  Maximum fronthaul capacity  & 200 bits/sec/Hz \\

@@

@@

Figure \ref{fig:8}, represents the aggregate throughput concerning the number of UEs in each service and the maximum power for three different mMTC service instances. mMTC service includes a large number of UEs with low data rates and low power. 
Assume each UE in each mMTC service instance requires $1bits/sec/Hz$ data rate and is not sensitive to the end-to-end delay. Also, suppose the fronthaul link has no restrictions. The figure depicts that by increasing the number of UEs in each instance of the service, the aggregate throughput increases. Also, by increasing the maximum power of each UE in each instance of mMTC service, the aggregate throughput rises too.
\begin{figure}
  %\centering 
    \includegraphics[scale = 0.4]{mmTCpower.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput for mMTC services vs. Number of UE in each Service for three different mMTC service instances}
  \label{fig:8}
\end{figure}

Assume we have two types of eMBB service instances. In figure \ref{fig:9}, the aggregate throughput (by considering the priority factor $\delta_s$) is depicted for two eMBB service instances. Here we consider 4 UEs in each service. We assume that the the fronthaul link and the end-to-end delay have no restrictions.
The figure \ref{fig:9} presented that by increasing the priority factor for one service instance, more resources are allocated to this service instance, and the aggregate throughput of this service is increased and vice versa. Also, we can realize from this figure that the aggregate throughput has the most significant value at the same priority.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{priorityLast.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput for two eMBB service instances vs. Priority of the first service instance }
  \label{fig:9}
\end{figure}
\section{Conclusion}\label{conc}
This paper proposed the downlink of the O-RAN system using network slicing for different types of 5G services (eMBB, mMTC, and URLC).
The isolation of various types of services (eMBB, mMTC, and URLC) in the O-DU, the O-CU, and the user plane function (UPF) is accomplished.
Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput. The limited fronthaul capacity and the mean end-to-end delay for each service are considered. 
The problem is mixed-integer non-linear programming that is solved by the two-step iterative algorithm.
In the first step, we reformulated the problem to achieve the number of activated VNFs as a function of data rate. Then we obtain PRB association and power allocation using the Lagrangian method.
Then in the second step, the O-RU association is acquired.
The performance of our proposed method (IABV) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
Also, we assume distinct scenarios for each service (eMBB, URLLC, and mMTC) based on their requirement QoS.
Simulation results depict that the proposed method (IABV) achieved $18.6\%$ higher data rate than the baseline scheme.
Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than FBDR and the baseline scheme.

>>>>

Virtualization technique for RAN and core is one of the exciting topics.  
In \cite{SystemCostMinimization,guo2016exploiting}, the authors solve the problem of obtaining beamforming and VMs activation in a C-RAN system with limited fronthaul capacity. 
This paper aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint. 
Also, transmission and processing delay are modeled based on M/M/1 queuing theory to guarantee delay for the UEs.
 In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also, the association of RRH to the UE is considered and solved using innovative methods.
In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
\subsection{Main Contribution}
This study aims to optimize baseband resource allocation (power allocation, PRB allocation, and O-RUs association) and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform. In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follow:
\begin{itemize}
\item In this paper, a network slicing model is depicted for three different types of services introduced in 5G i.e eMBB, mMTC, and URLLC. The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for a different types of services with specific QoS. 
\item The desired QoS conditions such as delay and throughput are considered for different types of services. We formulate the end-to-end mean delay of the system based on the number of activated VNFs and each user's throughput.
We consider the limited fronthaul capacity and accurately obtain the power and the capacity of each O-RU based on the quantization noise.
We model the interference of neighboring O-RU and formulate the actual throughput
for different types of services. We model the throughput of URLLC and mMTC based on their short packet transmission.
\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
We perform a two-step iterative algorithm to solve it.
The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
\end{itemize}

@@

Also, \eqref{c13} shows that the rate of each UE requesting each type of service i.e eMBB, mMTC, and URLLC is more than a threshold, respectively.

@@

So the the aggregate throughput is ascending function concerning the number of iterations and it will converge to the sub-optimal solution.

@@

In this section, numerical results for the main problem are depicted to evaluate the performance of the algorithms using the Monte-Carlo method. We consider three network slices for eMBB, URLLC, and mMTC services.

@@

Also the quantization noise is assumed to be $10^{-13}$.

@@

 Maximum transmit Power of each O-RU & 40dBm \\

@@

  Maximum fronthaul capacity  & 46 bits/sec/Hz \\

@@

Finding a feasible initial value is almost tricky. To overcome this challenge, we compare it with the baseline scheme method using the CVX of Matlab. If the baseline scheme converged and has a feasible solution, so our algorithm (IABV) can be converged too.

@@

Figure \ref{fig:8}, represents the aggregate throughput concerning the number of UEs in each service and the maximum power for three different mMTC service instances. mMTC service includes a large number of UEs with low data rates and low power. 
Assume each UE in each mMTC service instance requires 1bits/sec/Hz data rate and is not sensitive to the end-to-end delay. Also, suppose the fronthaul link has no restrictions. The figure depicts that by increasing the number of UEs in each instance of the service, the aggregate throughput increases. 
Also, by increasing the maximum power of each UE in each instance of mMTC service, the aggregate throughput rises too.
\begin{figure}
  %\centering 
    \includegraphics[scale = 0.4]{mmTCpower.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput for mMTC services vs. Number of UE in each Service for three different mMTC service instances}
  \label{fig:8}
\end{figure}

Assume we have two types of eMBB service instances. In figure \ref{fig:9}, the aggregate throughput (by considering the priority factor $\delta_s$) is depicted for two eMBB service instances. Here we consider 4 UEs in each service. We assume that the the fronthaul link and the end-to-end delay have no restrictions.
The figure \ref{fig:9} presented that by increasing the priority factor for one service instance, more resources are allocated to this service instance, and the aggregate throughput of this service is increased and vice versa. Also, we can realize from this figure that the aggregate throughput has the most significant value at the same priority.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{priorityLast.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput for two eMBB service instances vs. Priority of the first service instance }
  \label{fig:9}
\end{figure}

In the figure \ref{fig:10}, the aggregate throughput is presented vs. the number of UEs for one service in a system by considering two different cloud restrictions and fronthaul restrictions.
In the graph of cloud restriction, we have the restrictions in O-DU and O-CU.
In the graph of fronthaul restriction, we have the restrictions in O-RU.
In the O-RU restriction graph, we assume that the fronhaul link is set to be 43 bits/sec/Hz (the variance of quantization noise is $10^{-12}$) , and the maximum power of each O-RU is 40 dBm. Also, the maximum power of each UE is set to be 35 dBm. Moreover, the minimum data rate for each UE in this service is 6 bits/sec/Hz. In this graph, we assume that there is less restriction in the end-to-end delay (50 ms) and the VNF resources (the system has 100 reserved VNF).
In the graph of cloud restriction, we assume that there is no restriction on the fronthaul link.
The limitation on the power is less than the graph of fronthaul limitation, and it is set to be 45 dBm on the power of each O-RU, and the maximum power of each UE is 40 dBm.
The minimum data rate for each UE in this service is 6 bits/sec/Hz. 
The end-to-end delay for each UE is 4ms and the mean arrival rate is 2Mbps. 
and the mean service rate is 10Mbps.
In this figure, the consequence of cloud limitation and fronthaul limitation is depicted.
As the number of UEs increases, the aggregate throughput rises linearly, and the graph of cloud restriction increases more than the other graph of fronthaul limitation.

\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{cloudVsFronthaul.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput vs. Number of UE in a Service}
  \label{fig:10}
\end{figure}
\section{Conclusion}\label{conc}
This paper proposed the downlink of the O-RAN system using network slicing for different types of 5G services i.e eMBB, mMTC, and, URLLC.
The isolation of various types of services i.e eMBB, mMTC, and, URLLC in the O-DU, the O-CU, and the user plane function (UPF) is accomplished.
Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput. The limited fronthaul capacity and the mean end-to-end delay for each service are considered. 
The problem is mixed-integer non-linear programming that is solved by the two-step iterative algorithm.
In the first step, we reformulated the problem to achieve the number of activated VNFs as a function of data rate. Then we obtain PRB association and power allocation using the Lagrangian method.
Then in the second step, the O-RU association is acquired.
The performance of our proposed method (IABV) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
Also, we assume distinct scenarios for each service i.e eMBB, mMTC, and, URLLC based on their requirement QoS.
Simulation results depict that the proposed method (IABV) achieved $18.6\%$ higher data rate than the baseline scheme.
Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than FBDR and the baseline scheme.
